### 2021-03-16 README.Rmd

``` r
remotes::install_github("signaturescience/skater", auth_token = github_pat(quiet))
```

A GitHub [personal access token](https://github.com/settings/tokens) must be in the environment variable `GITHUB_PAT`.

>>>>

``` r
remotes::install_github("signaturescience/skater")
```

A GitHub [personal access token](https://github.com/settings/tokens) must be in the environment variable `GITHUB_PAT` or supplied as a string to `auth_token`. See `?remotes::install_github`.
